Measurement and Probability in Fuzzy Quantum Theories

### 2017-06-25 prop_iop.tex
prop_iop.tex \subsection{From Real-valued to Interval-valued} Updating..

\begin{example}For any positive integer~$n$, there is an additive
interval-valued function\nb$\widehat{\iota}_{n}:\left[0,1\right]\rightarrow\widehat{\mathscr{I}}_{n}$
defined by the following:
\begin{itemize}
\item when $x=0$ or $x=1$, $\widehat{\iota}_{n}\left(x\right)=\left[x,x\right]$;
\item when $0<x<1$, we have $\widehat{\iota}_{n}\left(x\right)=\left[\frac{k-1}{2n},\frac{k+1}{2n}\right]\cap\left[0,1\right]$,
where $k$ is defined by either one of the following:
\begin{itemize}
\item $2\mid k$ and $k-0.5\le2nx\le k+0.5$;
\item $2\nmid k$ and $k-0.5<2nx<k+0.5$,
\end{itemize}
\end{itemize}
where $\widehat{\mathscr{I}}_{n}=\set{\left[\frac{k-1}{2n},\frac{k+1}{2n}\right]\cap\left[0,1\right]}{k=0,\ldots,2n}\cup\left\{ \left[0,0\right],\left[1,1\right]\right\} $.\end{example}

@@

>>>>

\begin{example}\label{ex:equilateral}For any positive integer~$n$,
there is an additive interval-valued function\nb$\widehat{\iota}_{n}:\left[0,1\right]\rightarrow\widehat{\mathscr{I}}_{n}$
defined by the following:
\begin{itemize}
\item when $x=0$ or $x=1$, $\widehat{\iota}_{n}\left(x\right)=\left[x,x\right]$;
\item when $0<x<1$, we have $\widehat{\iota}_{n}\left(x\right)=\left[\frac{k-1}{2n},\frac{k+1}{2n}\right]\cap\left[0,1\right]$,
where $k$ is defined by either one of the following:
\begin{itemize}
\item $2\mid k$ and $k-0.5\le2nx\le k+0.5$;
\item $2\nmid k$ and $k-0.5<2nx<k+0.5$,
\end{itemize}
\end{itemize}
where $\widehat{\mathscr{I}}_{n}=\set{\left[\frac{k-1}{2n},\frac{k+1}{2n}\right]\cap\left[0,1\right]}{k=0,\ldots,2n}\cup\left\{ \left[0,0\right],\left[1,1\right]\right\} $.\end{example}

@@

The previous two lemmas can be applied on example~\ref{ex:equilateral},
we can estimate the states consistent with a QIVPM more tightly.

\begin{example}Given the additive interval-valued function\nb$\widehat{\iota}_{n}:\left[0,1\right]\rightarrow\widehat{\mathscr{I}}_{n}$,
the maximum length of intervals in $\widehat{\mathscr{I}}_{n}$ is
$1/n$, and $\min_{x\in\left(0,1\right)}\left\{ \max\widehat{\iota}_{n}\left(x\right)-x,x-\min\widehat{\iota}_{n}\left(x\right)\right\} =1/\left(4n\right)$.
Therefore, for any mixed state\nb$\rho$ such that .\end{example}
